Syntax and Semantics of Abstract Binding Trees

### 2015-11-12 paper.tex
[paper] write extension in pointful style

\begin{remark}
  A presheaf $P$ with a substitution monoidal structure $\Pair{\nu}{\varsigma}$
  also forms a \emph{relative monad}\footnote{Relative monads are skew-monoids
    in the skew-monoidal structure induced by a functor category
    $\mathbf{C}^\mathbf{J}$~\cite{altenkirch-chapman-uustalu:2015}. However,
    relative monads can also be understood without reference to monoids by
    viewing them as a generalization of \emph{extension systems} or
    \emph{Kleisli structures}. This latter presentation of monads, popular in
    computer science and logic, does not involve iteration of the monad
    functor.} on the functor $\Of{V}{\widehat{\HypCat}^\Sorts}$ of variables.
  Consequently, the monoid multiplication $\varsigma$ can be replaced with an
  extension operation $\Of{{(\,-\,)}^{\circledast}}{{\IMode{{P(\,=\,)}^{V(\,-\,)}}}\to{\IMode{{P(\,=\,)}^{P(\,-\,)}}}}$.
\end{remark}

>>>>

\begin{remark}
  A presheaf $P$ with a substitution monoidal structure $\Pair{\nu}{\varsigma}$
  also forms a \emph{relative monad}\footnote{Relative monads are skew-monoids
    in the skew-monoidal structure induced by a functor category
    $\mathbf{C}^\mathbf{J}$~\cite{altenkirch-chapman-uustalu:2015}. However,
    relative monads can also be understood without reference to monoids by
    viewing them as a generalization of \emph{extension systems} or
    \emph{Kleisli structures}. This latter presentation of monads, popular in
    computer science and logic, does not involve iteration of the monad
    functor.} on the functor $\Of{V}{\widehat{\HypCat}^\Sorts}$ of variables.
  Consequently, monoid multiplication $\varsigma$ can be replaced with extension
$\Of{\circledast}{\int_{\Tuple{\tau, (\Upsilon\parallel\Gamma), (\Upsilon'\parallel\Gamma')}}{{{P}_{\tau}(\Upsilon'\parallel\Gamma')}^{{V}_{\tau}(\Upsilon\parallel\Gamma)} \longrightarrow {{P}_{\tau}(\Upsilon'\parallel\Gamma')}^{{P}_{\tau}(\Upsilon\parallel\Gamma)}}}$.
\end{remark}
